Kids Moisture Summary

### 2020-03-16 demographics_summary.Rmd
New summary plots

---
title: "KidsAIR: household demographics summary"
author: "Ethan Walker"
date: "Started 27 Jan 2020, Updated 12 March 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

# Load individual datasets
```{r}
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")
demographics_clean <- read_rds("Output/demographics_clean.rds")
pm_clean <- read_rds("Output/pm_clean.rds")
```

# Filter for homes that have PM data
```{r}
# 93 Winter 1 placebo homes have PM data
pm_homes_placebo <- pm_clean %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime_new, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, pm_home) %>% 
  ungroup() %>% 
  arrange(area, home)

@@

# Summarize demographics data
```{r}
# Summarize numeric vars
kids_dems <- demographics_filtered %>%  
  mutate(total_residents = as.numeric(total_residents),
         residents_under_five = as.numeric(residents_under_five)) %>% 
  distinct(home, .keep_all = TRUE) %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(total_residents, na.rm = TRUE), 
            "SD" = sd(total_residents, na.rm = TRUE),
            "min" = min(total_residents, na.rm = TRUE), 
            "max" = max(total_residents, na.rm = TRUE))
kable(kids_dems, digits = 1, align = "c")

@@

demographics_filtered <- demographics_clean %>% 
  filter(winter_id == 1) %>% 
  filter(!is.na(hispanic_child)) %>% 
  mutate(income = factor(income,
                         levels = c("Less than $20,000", "$20,000 to $29,999",
                                    "$30,000 to $39,999", "$40,000 to $49,999",
                                    "$50,000 to $74,999", "$75,000 to $99,999",
                                    "$100,000 or more")),
         education = factor(education,
                            levels = c("Less than high school",
                                       "High school diploma or GED",
                                       "Some college",
                                       "College degree")))
```

@@

}

demographics_function(demographics_filtered, "gender_parent", "Parent sex", "count")
demographics_function(demographics_filtered, "hispanic_parent", "Parent Hispanic ethnicity", "count")
demographics_function(demographics_filtered, "race_parent", "Parent race", "count")
demographics_function(demographics_filtered, "hispanic_child", "Child Hispanic ethnicity", "count")
demographics_function(demographics_filtered, "race_child", "Child race", "count")
demographics_function(demographics_filtered, "age_child_nov", "Child age Nov 1st", "count")
demographics_function(demographics_filtered, "income", "Household income", "count")
demographics_function(demographics_filtered, "education", "Parent education", "count")
demographics_function(demographics_filtered, "total_residents", "Total residents", "count")
demographics_function(demographics_filtered, "residents_under_five", "Residents under 5", "count")
```

>>>>

---
title: "KidsAIR: household demographics summary"
author: "Ethan Walker"
date: "Started 27 Jan 2020, Updated 13 March 2020"
output: 
  powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, 
                      include = TRUE, warning = FALSE,
                      fig.height = 6, fig.width = 8)
```

@@

```{r}
# Load individual datasets

kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")
demographics_clean <- read_rds("Output/demographics_clean.rds")
pm_clean <- read_rds("Output/pm_clean.rds")
```

```{r}
# Filter for homes that have PM data

# 93 Winter 1 placebo homes have PM data
pm_homes_placebo <- pm_clean %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime_new, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, pm_home) %>% 
  ungroup() %>% 
  arrange(area, home)

@@

# Summarize demographics data
```{r, include=FALSE}
# Summarize numeric vars
kids_dems <- demographics_filtered %>%  
  mutate(total_residents = as.numeric(total_residents),
         residents_under_five = as.numeric(residents_under_five)) %>% 
  distinct(home, .keep_all = TRUE) %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(total_residents, na.rm = TRUE), 
            "SD" = sd(total_residents, na.rm = TRUE),
            "min" = min(total_residents, na.rm = TRUE), 
            "max" = max(total_residents, na.rm = TRUE))
kable(kids_dems, digits = 1, align = "c")

@@

demographics_filtered <- demographics_clean %>% 
  filter(winter_id == 1) %>% 
  filter(!is.na(hispanic_child)) %>% 
  mutate(income = factor(income,
                         levels = c("Less than $20,000", "$20,000 to $29,999",
                                    "$30,000 to $39,999", "$40,000 to $49,999",
                                    "$50,000 to $74,999", "$75,000 to $99,999",
                                    "$100,000 or more")),
         education = factor(education,
                            levels = c("Less than high school",
                                       "High school diploma or GED",
                                       "Some college",
                                       "College degree")),
         total_residents = as.numeric(total_residents),
         race_parent = factor(race_parent,
                              levels = c("American Indian/Alaskan Native",
                                         "Asian", "White",
                                         "More than one race"),
                              labels = c("AI/AN", "Asian", "White", "Multiple")),
         race_child = factor(race_child,
                              levels = c("American Indian/Alaskan Native",
                                         "White", "More than one race"),
                              labels = c("AI/AN", "White", "Multiple")))
```

@@

}
```

```{r}
demographics_function(demographics_filtered, "gender_parent", "Parent sex", "count")
```

\pagebreak

```{r}
demographics_function(demographics_filtered, "hispanic_parent", "Parent Hispanic ethnicity", "count")
```

\pagebreak

```{r}
demographics_function(demographics_filtered, "race_parent", "Parent race", "count")
```

\pagebreak

```{r}
demographics_function(demographics_filtered, "hispanic_child", "Child Hispanic ethnicity", "count")
```

\pagebreak

```{r}
demographics_function(demographics_filtered, "race_child", "Child race", "count")
```

\pagebreak

```{r}
demographics_function(demographics_filtered, "age_child_nov", "Child age Nov 1st", "count")
```

\pagebreak

```{r}
demographics_function(demographics_filtered, "income", "Household income", "count")
```

\pagebreak

```{r}
demographics_function(demographics_filtered, "education", "Parent education", "count")
```

\pagebreak

```{r}
demographics_function(demographics_filtered, "total_residents", "Total residents", "count")
```

\pagebreak

```{r}
demographics_function(demographics_filtered, "residents_under_five", "Residents under 5", "count")
```

### 2020-03-16 home_char_act_summary.Rmd
New summary plots

---
title: "Kids home characteristics/activity summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 27 Jan 2020"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, 
                      include = TRUE, warning = FALSE)
```

```{r, message=FALSE}
library(tidyverse)
library(readr)
library(knitr)
library(readxl)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
```

```{r}
# Load dataset
home_char_clean <- read_rds("Output/home_char_clean.rds") 
home_act_clean <- read_rds("Output/home_act_clean.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")
pm_clean <- read_rds("Output/pm_clean.rds")
```

# Summary data for home characteristics
```{r}
# Summarize numeric vars
home_char_summary <- home_char_clean %>% 
  #filter(winter_id == 1 | winter_id == 2) %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area) %>% 
  summarize("N" = n(),
            "Mean Sqft" = mean(home_sqft, na.rm = TRUE), 
            "SD Sqft" = sd(home_sqft, na.rm = TRUE), 
            "Min Sqft" = min(home_sqft, na.rm = TRUE), 
            "Median Sqft" = median(home_sqft, na.rm = TRUE), 
            "Max Sqft" = max(home_sqft, na.rm = TRUE))
kable(home_char_summary, digits = 1, align = "c")

@@

# Summary data for home activity
```{r}
# Summarize factor vars
## Use this as a quick look at all vars
table_list <- home_act_clean %>% 
  filter(winter_id == 1) %>% 
  #filter(area == "WMT") %>% 
  select(-home_winter_id, -home_act_comments, -home_id, -home, -treatment) 
#lapply(table_list, table)

@@

# Home characteristics summary plots
```{r}
home_char_function <- function(data, variable) {

@@

# Home activity summary plots
```{r}
home_act_function <- function(data, variable) {

@@

#### Abstract/manuscript tables ####

# Filter for homes that have PM data
```{r}
# 93 Winter 1 placebo homes have PM data
pm_homes_placebo <- pm_clean %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime_new, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, pm_home) %>% 
  ungroup() %>% 
  arrange(area, home)

@@

# Summarize home data
```{r}
# Summarize numeric vars
kids_char <- home_char_filtered %>%  
  distinct(home, .keep_all = TRUE) %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(home_furry, na.rm = TRUE), 
            "SD" = sd(home_furry, na.rm = TRUE),
            "min" = min(home_furry, na.rm = TRUE), 
            "max" = max(home_furry, na.rm = TRUE))
kable(kids_char, digits = 1, align = "c")

>>>>

---
title: "Kids home characteristics/activity summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 16 March 2020"
output:
  pdf_document: default
  powerpoint_presentation: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, 
                      include = TRUE, warning = FALSE,
                      fig.height = 5, fig.width = 7)
```

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(zoo)
library(knitr)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
```

```{r}
# Load dataset
home_char_clean <- read_rds("Output/home_char_clean.rds") %>% 
  mutate(chimney_clean = factor(chimney_clean,
                                levels = c("Less than 6 months ago",
                                           "6-12 months ago", "12-18 months ago",
                                           "More than 18 months ago"),
                                labels = c("< 6 months ago",
                                           "6-12 months ago", "12-18 months ago",
                                           "> 18 months ago")),
         stove_age = factor(stove_age,
                            levels = c("0-5 years old", "6-10 years old",
                                       "11-15 years old", "16 + years old",
                                       "Do not know")))

home_act_clean <- read_rds("Output/home_act_clean.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")
pm_clean <- read_rds("Output/pm_clean.rds")
```

```{r, include=FALSE}
# Summarize numeric vars
home_char_summary <- home_char_clean %>% 
  #filter(winter_id == 1 | winter_id == 2) %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area) %>% 
  summarize("N" = n(),
            "Mean Sqft" = mean(home_sqft, na.rm = TRUE), 
            "SD Sqft" = sd(home_sqft, na.rm = TRUE), 
            "Min Sqft" = min(home_sqft, na.rm = TRUE), 
            "Median Sqft" = median(home_sqft, na.rm = TRUE), 
            "Max Sqft" = max(home_sqft, na.rm = TRUE))
kable(home_char_summary, digits = 1, align = "c")

@@

```{r, include=FALSE}
# Summarize factor vars
## Use this as a quick look at all vars
table_list <- home_act_clean %>% 
  filter(winter_id == 1) %>% 
  #filter(area == "WMT") %>% 
  select(-home_winter_id, -home_act_comments, -home_id, -home, -treatment) 
#lapply(table_list, table)

@@

```{r, fig.height=8}
home_char_plot <- home_char_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, residents_smoke, residents_smoke_inside, home_damp:home_insert) %>% 
  pivot_longer(cols = c("residents_smoke":"home_insert"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  ggplot() +
    geom_bar(aes(value, fill = area)) +
    theme_minimal() +
    theme(strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 14, colour = "black", 
                                     angle = 25, vjust = 0.6),
          legend.text = element_text(size = 16, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, ncol = 2)
home_char_plot
```

```{r}
home_char_function <- function(data, variable) {

@@

```{r, fig.height=8}
home_act_plot <- home_act_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, home_act_gas:home_act_sweep) %>% 
  pivot_longer(cols = c("home_act_gas":"home_act_sweep"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  ggplot() +
    geom_bar(aes(value, fill = area)) +
    theme_minimal() +
    theme(strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 14, colour = "black", 
                                     angle = 25, vjust = 0.6),
          legend.text = element_text(size = 16, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, ncol = 2)
home_act_plot
```

```{r}
home_act_function <- function(data, variable) {

@@

```{r, include=FALSE}
#### Abstract/manuscript tables ####

# Filter for homes that have PM data

# 93 Winter 1 placebo homes have PM data
pm_homes_placebo <- pm_clean %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime_new, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, pm_home) %>% 
  ungroup() %>% 
  arrange(area, home)

@@

```{r, include=FALSE}
# Summarize numeric vars
kids_char <- home_char_filtered %>%  
  distinct(home, .keep_all = TRUE) %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(home_furry, na.rm = TRUE), 
            "SD" = sd(home_furry, na.rm = TRUE),
            "min" = min(home_furry, na.rm = TRUE), 
            "max" = max(home_furry, na.rm = TRUE))
kable(kids_char, digits = 1, align = "c")

### 2020-03-16 indoor_temp_rh_summary.Rmd
New summary plots

---
title: "Kids indoor temp/RH summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 23 Jan 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, 
                      include = TRUE, warning = FALSE)
```

```{r, message=FALSE}
library(tidyverse)
library(readr)
library(knitr)
```

```{r}
# Load data
indoor_temp_rh_clean <- read_rds("Output/indoor_temp_rh_clean.rds")
```

# Summary stats
```{r}
temp_rh_summary <- indoor_temp_rh_clean %>%
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area) %>% 
  summarize_if(is.numeric, list(mean = mean, sd = sd, min = min, 
                                med = median, max = max), na.rm = TRUE) %>% 
  select(-area) %>% 
  t() 
kable(temp_rh_summary, col.names = c("Alaska", "Navajo", "Montana"), 
      digits = 1, align = "c")
```

```{r, fig.height=6, fig.width=5}
# Boxplot function
boxplots_temp_rh_function <- function(data, variable){

boxplots_temp_rh <- data %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, variable) %>% 
  rename(plot_var = variable) %>% 
  na.exclude() %>% 
  ggplot(aes(area, plot_var)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_temp_rh

@@

## Current indoor humidity (%)
```{r}
boxplots_temp_rh_function(indoor_temp_rh_clean, "rh_indoor_current")
```

## Max indoor humidity (%)
```{r}
boxplots_temp_rh_function(indoor_temp_rh_clean, "rh_indoor_max")
```

## Min indoor humidity (%)
```{r}
boxplots_temp_rh_function(indoor_temp_rh_clean, "rh_indoor_min")
```

## Current indoor temperature (C)
```{r}
boxplots_temp_rh_function(indoor_temp_rh_clean, "temp_indoor_current")
```

## Max indoor temperature (C)
```{r}
boxplots_temp_rh_function(indoor_temp_rh_clean, "temp_indoor_max")
```

## Min indoor temperature (C)
```{r}
boxplots_temp_rh_function(indoor_temp_rh_clean, "temp_indoor_min")
```

>>>>

---
title: "Kids indoor temp/RH summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 16 March 2020"
output:
  powerpoint_presentation: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, 
                      include = TRUE, warning = FALSE,
                      fig.height = 5, fig.width = 7)
```

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(zoo)
library(knitr)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
```

```{r}
# Load data
indoor_temp_rh_clean <- read_rds("Output/indoor_temp_rh_clean.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")
pm_clean <- read_rds("Output/pm_clean.rds")
```

```{r, include=FALSE}
temp_rh_summary <- indoor_temp_rh_clean %>%
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area) %>% 
  summarize_if(is.numeric, list(mean = mean, sd = sd, min = min, 
                                med = median, max = max), na.rm = TRUE) %>% 
  select(-area) %>% 
  t() 
kable(temp_rh_summary, col.names = c("Alaska", "Navajo", "Montana"), 
      digits = 1, align = "c")
```

```{r, fig.height=6, fig.width=5}
# Boxplot function
boxplots_temp_rh_function <- function(data, var, title_label, y_label){

temp_rh_plot <- data %>% 
    filter(winter_id == 1) %>% 
    select(area, var) %>% 
    rename(plot_var = var) %>% 
    filter(!is.na(plot_var)) %>% 
    ggplot(aes(area, plot_var)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red",
                 position=position_nudge(x = -0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=mean, geom="text", 
                 size=7, position=position_nudge(x = -0.35, y = 0)) +
    stat_summary(fun.y=median, geom="point", shape=16, size=4, color="blue",
                 position=position_nudge(x = 0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=median, geom="text", 
                 size=7, position=position_nudge(x = 0.35, y = 0)) +
    theme_minimal() +
    labs(title = title_label, subtitle = "Mean = Red, Median = Blue") +
    ylab(y_label) +
    theme(title = element_text(size = 20, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) 
  temp_rh_plot

@@

```{r}
boxplots_temp_rh_function(indoor_temp_rh_clean, "rh_indoor_current", 
                          "Current indoor humidity", "%")
```

```{r}
boxplots_temp_rh_function(indoor_temp_rh_clean, "rh_indoor_max", 
                          "Max indoor humidity", "%")
```

```{r}
boxplots_temp_rh_function(indoor_temp_rh_clean, "rh_indoor_min", 
                          "Min indoor humidity", "%")
```

```{r}
boxplots_temp_rh_function(indoor_temp_rh_clean, "temp_indoor_current", 
                          "Current indoor temperature", "Degrees C")
```

```{r}
boxplots_temp_rh_function(indoor_temp_rh_clean, "temp_indoor_max", 
                          "Max indoor temperature", "Degrees C")
```

```{r}
boxplots_temp_rh_function(indoor_temp_rh_clean, "temp_indoor_min", 
                          "Min indoor temperature", "Degrees C")
```

```{r}
#### Abstract/manuscript tables ####

# Filter for homes that have PM data

# 93 Winter 1 placebo homes have PM data
pm_homes_placebo <- pm_clean %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime_new, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, pm_home) %>% 
  ungroup() %>% 
  arrange(area, home)

temp_rh_filtered <- indoor_temp_rh_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes_placebo, by = c("area", "home", "home_winter_id")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  ungroup() %>% 
  arrange(area, home)
```

```{r, include=FALSE}
# Summarize numeric vars
kids_temp_rh <- temp_rh_filtered %>%  
  distinct(home, .keep_all = TRUE) %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(rh_indoor_min, na.rm = TRUE), 
            "SD" = sd(rh_indoor_min, na.rm = TRUE),
            "min" = min(rh_indoor_min, na.rm = TRUE), 
            "med" = median(rh_indoor_min, na.rm = TRUE), 
            "max" = max(rh_indoor_min, na.rm = TRUE))
kable(kids_temp_rh, digits = 1, align = "c")

```

### 2020-03-16 moisture_summary.Rmd
New summary plots

---
title: "Kids Moisture Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated 28 Jan 2020"
output: pdf_document
---

@@

```{r, message=FALSE}
library(tidyverse)
library(lubridate)
library(readr)
library(knitr)
```

@@

# Moisture content summary stats
## Average of 3 measurements
```{r}
summary_moisture <- moisture_clean %>%
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area) %>% 
  summarize(mean = mean(moisture_ave, na.rm = TRUE), 
            SD = sd(moisture_ave, na.rm = TRUE),
            median = median(moisture_ave, na.rm = TRUE),
            min = min(moisture_ave, na.rm = TRUE), 
            max = max(moisture_ave, na.rm = TRUE)) %>%
  select(-area) %>% 
  t() 
kable(summary_moisture, col.names = c("Alaska", "Navajo", "Montana"), 
      digits = 1, align = "c")
```

# Was wood split?
```{r}
wood_split <- moisture_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(!is.na(moisture_split)) %>% 
  group_by(area, moisture_split) %>% 
  summarise(n = n())
kable(wood_split, align = "c")
```

# Boxplots
```{r, fig.height=6, fig.width=5}
boxplots_moisture <- moisture_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, moisture_ave) %>% 
  na.exclude() %>% 
  ggplot(aes(area, moisture_ave)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=3, color="red") +
    theme_minimal() +
    ylim(0, 50) +
    #geom_hline(yintercept = 50, color = "red", size = 1.2) +
    labs(y = "Mean moisture content (%)") +
    #labs(aes(x = "", y = paste("48-hour indoor PM "[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_moisture
```

#### Abstract/manuscript tables ####

# Filter for homes that have PM data
```{r}
# 93 Winter 1 placebo homes have PM data
pm_homes_placebo <- pm_clean %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime_new, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, pm_home, first_datetime_new) %>% 
  separate(first_datetime_new, c("first_date", "first_time"), sep = " ", remove = TRUE) %>% 
  ungroup() %>% 
  arrange(area, home)

@@

# Summarize home data
```{r}
# Summarize numeric vars
kids_moisture <- moisture_filtered %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(moisture_ave, na.rm = TRUE), 
            "SD" = sd(moisture_ave, na.rm = TRUE),
            "min" = min(moisture_ave, na.rm = TRUE), 
            "med" = median(moisture_ave, na.rm = TRUE), 
            "max" = max(moisture_ave, na.rm = TRUE))
kable(kids_moisture, digits = 1, align = "c")

>>>>

---
title: "Kids Moisture Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated 16 March 2020"
output: powerpoint_presentation
---

@@

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(zoo)
library(knitr)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
```

@@

```{r, include=FALSE}
# Moisture content summary stats
## Average of 3 measurements

summary_moisture <- moisture_clean %>%
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area) %>% 
  summarize(mean = mean(moisture_ave, na.rm = TRUE), 
            SD = sd(moisture_ave, na.rm = TRUE),
            median = median(moisture_ave, na.rm = TRUE),
            min = min(moisture_ave, na.rm = TRUE), 
            max = max(moisture_ave, na.rm = TRUE)) %>%
  select(-area) %>% 
  t() 
kable(summary_moisture, col.names = c("Alaska", "Navajo", "Montana"), 
      digits = 1, align = "c")
```

```{r, include=FALSE}
wood_split <- moisture_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  filter(!is.na(moisture_split)) %>% 
  group_by(area, moisture_split) %>% 
  summarise(n = n())
kable(wood_split, align = "c")
```

```{r, fig.height=6, fig.width=7}
boxplots_moisture <- moisture_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, moisture_ave) %>% 
  na.exclude() %>% 
  ggplot(aes(area, moisture_ave)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red",
                 position=position_nudge(x = -0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=mean, geom="text", 
                 size=7, position=position_nudge(x = -0.35, y = 0)) +
    stat_summary(fun.y=median, geom="point", shape=16, size=4, color="blue",
                 position=position_nudge(x = 0.1, y = 0)) +
    stat_summary(aes(label=round(..y.., digits = 1)), fun.y=median, geom="text", 
                 size=7, position=position_nudge(x = 0.35, y = 0)) +
    theme_minimal() +
    ylim(0, 50) +
    labs(title = "Mean wood moisture content") +
    labs(y = "%") +
    theme(axis.text.x = element_text(size = 16, colour = "black"),
          title = element_text(size = 20, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_moisture
```

```{r, fig.height=6, fig.width=7}
bar_plot <- moisture_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, moisture_split) %>% 
  ggplot() +
    geom_bar(aes(moisture_split, fill = area)) +
    theme_minimal() +
    labs(title = "Was wood split?") +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          title = element_text(size = 20, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    scale_fill_manual(values = jv_palette)
bar_plot
```

```{r}
#### Abstract/manuscript tables ####

# Filter for homes that have PM data

# 93 Winter 1 placebo homes have PM data
pm_homes_placebo <- pm_clean %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  mutate(initial_obs = if_else(pm_datetime_new == first_datetime_new, 1, 0)) %>% 
  filter(initial_obs == 1) %>% 
  mutate(pm_home = "true") %>% 
  select(area, home, home_winter_id, pm_home, first_datetime_new) %>% 
  separate(first_datetime_new, c("first_date", "first_time"), sep = " ", remove = TRUE) %>% 
  ungroup() %>% 
  arrange(area, home)

@@

```{r, include=FALSE}
# Summarize numeric vars
kids_moisture <- moisture_filtered_time %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(moisture_ave, na.rm = TRUE), 
            "SD" = sd(moisture_ave, na.rm = TRUE),
            "min" = min(moisture_ave, na.rm = TRUE), 
            "med" = median(moisture_ave, na.rm = TRUE), 
            "max" = max(moisture_ave, na.rm = TRUE))
kable(kids_moisture, digits = 1, align = "c")
